SETI in the Spatial-Temporal Survey Domain

### 2019-04-17 paper/ms.tex
start writing Section 4

we need to be looking at big optical surveys, since they provide such amazing sky/time coverage

bright facilities have excellent sky and time coverage:
ASAS-SN \citep{kochanek2017}

@@

space-based platforms designed for exoplanet searches provide very high quality light curves over months to years timescales. The \Kepler and K2 missions \citep{borucki2010,howell2014} produced 30-minute cadence light curves for $\sim$500,000 stars, with baselines ranging from $\sim$3 months up to 4 years. 
and TESS \citep{tess}, as well as Gaia \citep{gaia} provide incredible precision light curves for millions of stars.

RNAAS about tools to model technosignatures from radio surveys
\citep{forgan2019}

\begin{figure}[]
\centering
\includegraphics[width=3.5in]{../figures/optical_haystack}
\caption{
comparison of the 8D ``Cosmic Haystack'' volume defined by \citet{wright2018c} using four optical surveys with varying designs. 
}
\label{fig:hay}
\end{figure}

>>>>

\citet{wright2018c} have provided a framework to quantify the volume of observable parameter space covered by various SETI projects -- dubbed the ``Cosmic Haystack''. The properties for several major radio SETI projects yield a Haystack volume coverage of $10^{-20}$ to $10^{-18}$, or as \citet{wright2018c} illustrate, akin to a drinking glass of water compared to the volume of Earth's oceans. While this tool was developed with radio surveys in mind, it is broadly applicable to surveys at other wavelengths that are not explicitly designed for SETI \citep[e.g. see][]{forgan2019}.

While the potential for optical time domain surveys to advance technosignature searches has been qualitatively laid out in \S\ref{sec:method}, it is useful to quantitatively compare their capability to traditional searches in the radio. 
For typical optical surveys using broadband photometry \citep{djorgovski2013}, the key parameters that determine the Cosmic Haystack volume coverage are the sky coverage ($\Omega$ in sq deg), total integration time per target ($T$ in sec), and survey sensitivity or per-epoch depth ($S$ in Jy).
%we need to be looking at big optical surveys, since they provide such amazing sky/time coverage

@@

%space-based platforms designed for exoplanet searches provide very high quality light curves over months to years timescales. The \Kepler and K2 missions \citep{borucki2010,howell2014} produced 30-minute cadence light curves for $\sim$500,000 stars, with baselines ranging from $\sim$3 months up to 4 years. 
and TESS \citep{tess}, as well as Gaia \citep{gaia} provide incredible precision light curves for millions of stars.

\begin{figure}[]
\centering
\includegraphics[width=3.5in]{../figures/optical_haystack}
\caption{
comparison of the 8D ``Cosmic Haystack'' volume defined by \citet{wright2018c} using five optical surveys with varying designs. 
}
\label{fig:hay}
\end{figure}
